---
title: "Tooth Growth"
author: "Andrea Castagna"
date: "8/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Effect of Vitamin C on Tooth Growth in Guinea Pigs

# Basic Inferential Data Analysis

# Main question: DO DELIVERY METHOD AND/OR DOSAGE AFFECT TOOTH GROWTH IN GUINEA PIGS?

# 1.Overview 

_The Tooth Growth data set contains information about an experiment regarding odontoblasts cells in 60 guinea pigs._

_The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs._
_Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day)_
_by one of two delivery methods, orange juice or ascorbic acid (a form of vitamin C and coded as VC)._


```{r Loading the Dataset & Packets}

library(ggplot2)
library(ggpubr)
library(tidyr)
library(stringr)
library(dplyr)

data("ToothGrowth")

head(ToothGrowth)

tail(ToothGrowth)

str(ToothGrowth)

```

_Tooth Growth is  data frame with 60 observations on 3 variables._

 1. len  _numeric_	 *Tooth length*
 2. supp _factor_	   *Supplement type (VC or OJ)*
 3. dose _numeric_	 *Dose in milligrams/day*

_Source_

_C. I. Bliss (1952). The Statistics of Bioessay. Academic Press._

_References_

_McNeil, D. R. (1977). Interactive Data Analysis. New York: Wiley._
_Crampton, E. W. (1947). The growth of the odontoblast of the incisor teeth as a criterion of vitamin C intake of the guinea pig. The Journal of Nutrition, 33(5), 491–504. doi: 10.1093/jn/33.5.491._

# 1.2 Exploratory Data Analysis 

```{r Initial Graphics and Distribution}

# Overlaid histograms with means
plot1 <- ggplot(ToothGrowth, aes(x=len, y=dose, fill=supp)) +geom_bar(alpha=.5, stat = "identity")

plot1

plot2 <- quickplot(dose, len, data = ToothGrowth, colour=supp)

plot2

plot3 <- ggplot(ToothGrowth, aes(x=len,fill=supp)) +geom_bar(alpha=.5)

plot3

quicksummary <-ToothGrowth %>% group_by(supp) %>% summarize(count = n())

orangejuice <- ToothGrowth %>% filter(supp == "OJ")

ascorbicacid <- ToothGrowth %>% filter(supp == "VC")
