---
title: "Tooth Growth"
author: "Andrea Castagna"
date: "8/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Effect of Vitamin C on Tooth Growth in Guinea Pigs

# Basic Inferential Data Analysis

# Main question: DO DELIVERY METHOD AND/OR DOSAGE AFFECT TOOTH GROWTH IN GUINEA PIGS?

# Overview 

_The Tooth Growth data set contains information about an experiment regarding odontoblasts cells in 60 guinea pigs._

_The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs._
_Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day)_
_by one of two delivery methods, orange juice or ascorbic acid (a form of vitamin C and coded as VC)._


```{r Loading the Dataset}

data("ToothGrowth")

head(ToothGrowth)

tail(ToothGrowth)

str(ToothGrowth)

```

_Tooth Growth is  data frame with 60 observations on 3 variables._

 1. len  _numeric_	 *Tooth length*
 2. supp _factor_	   *Supplement type (VC or OJ)*
 3. dose _numeric_	 *Dose in milligrams/day*

_Source_
_C. I. Bliss (1952). The Statistics of Bioessay. Academic Press._


